\tool: Revisiting BadUSB with Type-C

### 2021-03-10 WOOT/Files/introduction.tex

The \ac{USB} protocol has become popular worldwide
since its appearance\shuqing{When?}, as it provides a unified and easy-to-use approach for a
extensive range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

@@

BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
are conducted by modifying the device firmware, which are disguised
 as ordinary \ac{USB} devices as other types of devices that are \textit{trust-by-default}
by the hosts.  Typically, simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
attackers can pretend to be regular users, typing malicious commands to
victims' computers, downloading and executing malicious scripts, and copying out
private data from disks.  Such attacks can easily \shuqing{arg1} get detected by from traditional
anti-virus software since it is hard to distinguish them from ordinary \ac{USB}
devices.

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers cannot obtain the current \ac{UI} status, limiting
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns like buttons and links on victim
computers by disguising \ac{USB} devices like mice.  That explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the host network usage.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a more extensive range of
peripherals such as DisplayPort, HDMI and PowerDelivery.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.0.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
victim's graphical interface during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.  
Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers are involved in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information, demonstrating the \shuqing{importance of our re?}.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

>>>>

The \ac{USB} protocol has become popular worldwide
since its appearance in 1996, as it provides a unified and easy-to-use approach for a
extensive range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

@@

BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
are conducted by modifying the device firmware, which are disguised
 as ordinary \ac{USB} devices as other types of devices that are \textit{trust-by-default}
by the hosts.  Typically, simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
attackers can pretend to be regular users, typing malicious commands to
victims' computers, downloading and executing malicious scripts, and copying out
private data from disks.  Such attacks can easily avoid detection by traditional
anti-virus software since it is hard to distinguish them from ordinary \ac{USB}
devices.

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers cannot obtain the current \ac{UI} status, limiting
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns such as buttons and links on victim
computers by disguising \ac{USB} devices, e.g., mice.  This explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the host network usage.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a more extensive range of
peripherals such as DisplayPort, HDMI and PowerDelivery.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.x.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a \ac{GUI} for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
victim's graphical interface during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.  
Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers are involved in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}
